Intensity Modulated Radiation Therapy using Tomotherapy

### 2014-12-01 BME 560/Paper.tex
Introduction updated

  Tomotherapy was designed in the University of Wisconsin - Madison and 
  TomoTherapy Inc., Madison, WI. The first prototype investigated in this study 
  was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
  USA. 
  The setup has a linear accelerator mounted on a rotating gantry as seen in CT 
  sacnners. The radiation is delivered to a patient in a helical way, obtained 
  by concurrent gantry rotation and couch/patient travel as shown in Fig. 
  \ref{fig1}. In general, the helical tomotherapy units have significantly 
  different radiation fields when compared to other radiotherapy systems. This 
  difference can be owed to the absence of absence of a flattening filter, a 
  thin target, an electron stopper, a beam hardener and a compact primary 
  collimator. And for this reason, this paper will briefly highlight the 
  radiation characteristics of the helical tomotherapy unit, especially in 
  parts where it differs from standard accelerators.
  \begin{figure*}[t!]
	\includegraphics[width=\linewidth]{fig1}
  \label{fig1}
  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
  diagram showing the ring gantry, and the radiation source}
  \end{figure*}
	%----------------------------------
	% References
  %----------------------------------

>>>>

  Tomotherapy was designed in the University of Wisconsin - Madison and 
  TomoTherapy Inc., Madison, WI. The first prototype investigated in this study 
  was installed at University of Wisconsin Hospital and Clinics in Madison, WI, 
  USA. The first paper on tomotherapy was submitted in 1992, Ref. 
  \cite{Mackie1993}. This paper described most of the details seen in the 
  modern sytems in use today. This paper also introducted the idea of using a 
  continuously moving slip-ring gantry. The usage of fan-beam to form a 
  modulating beam, and a temorally modulating collimator assembly (this came 
  to be known as the `Binary Collimator').

  The setup has a linear accelerator mounted on a rotating gantry as seen in CT 
  sacnners. The radiation is delivered to a patient in a helical way, obtained 
  by concurrent gantry rotation and couch/patient travel as shown in Fig. 
  \ref{fig1}. In general, the helical tomotherapy units have significantly 
  different radiation fields when compared to other radiotherapy systems. This 
  difference can be owed to the absence of absence of a flattening filter, a 
  thin target, an electron stopper, a beam hardener and a compact primary 
  collimator. And for this reason, this paper will briefly highlight the 
  radiation characteristics of the helical tomotherapy unit, especially in 
  parts where it differs from standard accelerators.
  \begin{figure*}[t!]
  	\includegraphics[width=\linewidth]{fig1}
  \label{fig1}
  \caption{A traditional tomotherapy unit, Ref \cite{Mackie1993}. (a) A block 
  diagram showing the ring gantry, and the radiation source}
  \end{figure*}
	%----------------------------------
	% References
  %----------------------------------
